R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-07 manuscript.Rmd
forget about python and ruby on circleci, eval=false for all python and ruby chunks
one more eval=false for a ruby chunk

```{python}
from pygbif import registry
registry.dataset_metrics(uuid='ec93a739-1681-4b04-b62f-3a687127a17f')
```

@@

```{python}
from pygbif import registry
registry.networks(limit = 10)
```

@@

```{ruby}
require 'gbifrb'
registry = Gbif::Registry
registry.networks(limit: 10)
```

>>>>

```{python eval=FALSE}
from pygbif import registry
registry.dataset_metrics(uuid='ec93a739-1681-4b04-b62f-3a687127a17f')
```

@@

```{python eval=FALSE}
from pygbif import registry
registry.networks(limit = 10)
```

@@

```{ruby eval=FALSE}
require 'gbifrb'
registry = Gbif::Registry
registry.networks(limit: 10)
```
